emmeans and varpred comparison

### 2021-10-11 compare_emmeans_varpred.rmd
Package documentation

vplots <- vareffects:::plot.vareffects

@@

```{r catni, fig.cap="Categorical: no interaction"}
compare_catni_plots <- (combinepreds(mod_catni, focal="gender"
		, funs=c("emmeans", "varpred")
		, x.var="gender"
		, x.var.factor=TRUE
		, plotit=TRUE
	)
	+ geom_point(data=focal_prop_catni, aes(x=gender, y=hhsize), colour="black")
)
print(compare_catni_plots)
```

>>>>

within.category <- TRUE

@@

```{r catni, fig.cap="Categorical: no interaction"}
compare_catni_plots <- (combinepreds(mod_catni, focal="gender"
		, funs=c("emmeans", "varpred")
		, x.var="gender"
		, within.category=within.category
		, x.var.factor=TRUE
		, plotit=TRUE
	)
	+ geom_point(data=focal_prop_catni, aes(x=gender, y=hhsize), colour="black")
)
print(compare_catni_plots)
```
